Conceptual and methodological problems with bias detection and avoidance in natural language processing

### 2021-06-08 thesis/index.Rmd
Merge branch 'main' of github.com:rfl-urbaniak/BayesBias

---
title: "Conceptual and methodological problems with bias detection and avoidance in natural language processing"
author: "Alicja Dobrzeniecka"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_book: 
    keep_tex: yes
    toc_depth: 6
    latex_engine: xelatex
  bookdown::gitbook:
    lib_dir: "book_assets"
includes:
    in_header:
      - Rafal_latex6.sty
documentclass: book
classoptions: dvipsnames, usenames
site: bookdown::bookdown_site
bibliography: [../references/bibliographyRafal.bib]
biblio-style: 
link-citations: yes
csl: apa-5th-edition.csl
---

@@

# Preface {-}

Test

>>>>

---
title: "Conceptual and methodological problems with bias detection and avoidance in natural language processing"
author: "Alicja Dobrzeniecka"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_book: 
    keep_tex: yes
    toc_depth: 6
    latex_engine: xelatex
    extra_dependencies: ["todonotes"]
  bookdown::gitbook:
    lib_dir: "book_assets"
includes:
    in_header:
      - Rafal_latex6.sty
documentclass: book
classoptions: dvipsnames, usenames
site: bookdown::bookdown_site
bibliography: [../references/bibliographyRafal.bib]
biblio-style: 
link-citations: yes
fontsize: 12pt
linestretch: 1.5
geometry: left=3.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm, asymmetric, includeheadfoot
csl: apa-5th-edition.csl
---

@@

<!-- # Preface {-} -->

<!-- Test  -->
